
%\subsection{Case Study}
\noindent\textbf{Case Study.}
\label{casestudy}
From this case study we demonstrate the effectiveness of \ring for multi-granularity, multi-aspect event monitoring that it can tell the story of an event automatically.
An event's evolution chain distilled by \ring is shown in Table~\ref{fig:evolution}.
Given (by search or trending event ranking interface) the ``latest'' event in the table, an evolution chain that spans several month was revealed.
These events are about the second trial of the infamous poisoning case in Fudan University, China
where the suspect poisoned his roommate to death in April 2013.
The detected events are all significant in its development and we can see that forecast, process and judgement of the trial all drew a lot of attention, hence detected by \ring.
The descriptions of these events are extracted automatically either directly from tweets or from representative tweets that contained predefined brackets indicating proper titles.
Recall from~\ref{detection} that our system reports trending events in 10-minute intervals.
Each of these events in Table~\ref{fig:evolution} has been repeatedly detected in consecutive time intervals, lasting from 20 minutes to 60 minutes.
It is indicated by trending keywords detection algorithm that a consecutive exponential growth of tweets in volume has been detected.
The system consolidate such similar events to show only one such event and highlight such event for special attention.
We manually inspect the average latency of detection of these events, i.e. the time from the first tweet appearing in our data to the detection time, to be 14.4 minutes, which is shown in the table.
%A event evolution case is shown in Figure \ref{fig:evolution}. All the events are detected using our method proposed in Section \ref{detection}.

%Our algorithm can trace all the developmental stages of this case's second trial as you can see from the table, even though they spans over several months.
The sub-event hierarchy of the first event in Table~\ref{fig:evolution} is shown in Table~\ref{fig:subevent}.
There are two aspects of the event.
The first is about the suspect writing an apology letter to the victim's parents and the other is that the second trial of the poison case is scheduled to be held in Shanghai, showing different aspects as history and current development of the event.

